\documentclass[10pt]{article}

\usepackage{graphicx,amsmath,amssymb,color}

\addtolength{\oddsidemargin}{-.875in}
\addtolength{\evensidemargin}{-.875in}
\addtolength{\textwidth}{1.75in} \addtolength{\topmargin}{-.9in}
\addtolength{\textheight}{2.75in}

\pagestyle{empty} \setlength{\parindent}{0pt}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand\note[1]{\mbox{}\marginpar{\footnotesize\raggedright\hspace{0pt}\color{blue}\bf{#1}}}

\newenvironment{changemargin}[2]{%
  \list{}{\rightmargin#2\leftmargin#1
    \parsep=0pt\topsep=1pt\partopsep=0pt}
\item[]} {\endlist}

\newenvironment{indentmore}{\begin{changemargin}{10pt}{0cm}}{\end{changemargin}}

\begin{document}

\begin{center}

\textbf{\Large Perry W.M. Ellis}
\HRule

44 Hancock Street, Apt 3, Somerville, MA 02144 $\bullet$ 949.309.0360 $\bullet$ perrywmellis@gmail.com

\end{center}

%\textbf{\large OBJECTIVE}\\
%Obtain a job requiring the application of lateral thinking and problem solving skills to a wide variety of problems on a daily basis.  Interested in cross-disciplinary work requiring and encouraging continuous learning.
\vspace{10pt}
\textbf{\large EMPLOYMENT} \\
\textbf{Harvard University}, Cambridge, MA\\
\hspace*{10pt}Postdoctoral Fellow \hfill September 2018 -- Present\\
\hspace*{10pt}Advisor: David. A Weitz
\vspace{10pt}

\textbf{\large EDUCATION} \\
\textbf{Georgia Institute of Technology}, Atlanta, GA\\
\hspace*{10pt}Ph.D., Physics, G.P.A. 3.9/4.0 \hfill May 2018\\
\hspace*{10pt}Advisor: Alberto Fernandez-Nieves\\
\hspace*{10pt}Dissertation: \emph{Nematic materials in curved spaces}\\

\hspace*{10pt}Master of Science, Physics, G.P.A 3.9/4.0 \hfill December 2012
%\begin{indentmore}\textit{Honors and Awards:} Member, Gamma Beta Phi, Georgia Tech Chapter, Spring 2012-Present
%\end{indentmore}
%\begin{indentmore}\textit{Relevant Courses:}
%Digital Image Processing $\bullet$
%Electromagnetism I \& II
%$\bullet$ Quantum Mechanics I \& II $\bullet$ Classical Mechanics I $\bullet$
%Statistical Mechanics I
%$\bullet$ Soft Matter
%$\bullet$ Mathematical Methods
%\end{indentmore}

\vspace{10pt}

\textbf{Harvey Mudd College}, Claremont, CA \\
\hspace*{10pt}Bachelor of Science, Physics, G.P.A. 3.4/4.0 \hfill May 2011
%\begin{indentmore}\textit{Relevant Courses:}
%Electrodynamics $\bullet$
%Electromagnetic Fields
%$\bullet$ Theoretical Mechanics $\bullet$
%Statistical Mechanics
%$\bullet$ Fourier Series and Boundary Value Problems
%$\bullet$ Quantum Mechanics $\bullet$ Advanced Laboratory $\bullet$ Electronics Laboratory $\bullet$ Modern Physics Laboratory $\bullet$ Design Realization and Representation
%\end{indentmore}
%\begin{indentmore}
%\textit{Honors and Awards:} National Merit Scholar, 2007-2011 $\bullet$ Harvey Mudd Merit Scholarship, 2007-2011 \\ \hspace*{5pt}$\bullet$ Harvey Mudd College Dean's List, Spring 2008, 2009, 2011, Fall 2009, 2010
%\end{indentmore}

\vspace{5pt}
\textbf{Study Abroad} \\
\hspace*{10pt}University of Granada, Granada, Spain \hfill Spring 2010\\


\textbf{\large HONORS AND AWARDS}
\begin{indentmore}

Sigma Xi Research Award - Best PhD Thesis, Georgia Institute of Technology, 2019 $\bullet$ FLAMEL Doctoral Fellowship, Georgia Institute of Technology, Fall 2015 -- Summer 2017 $\bullet$  Member, Gamma Beta Phi, Georgia Institute of Technology Chapter, Summer 2012 -- Spring 2014 $\bullet$ National Merit Scholar, 2007 -- 2011 $\bullet$ Harvey Mudd Merit Scholarship, 2007 -- 2011 $\bullet$ Harvey Mudd College Dean's List, Spring 2008, 2009, 2011, Fall 2009, 2010
\end{indentmore}

\vspace{10pt}
\textbf{\large PUBLICATIONS}
\begin{indentmore}
DJG Pearce, J. Nambisan, \underline{P.W. Ellis},  A. Fern\'{a}ndez-Nieves, L. Giomi, \emph{Orientational correlations \\ \hspace*{15pt} in active and passive nematic defects}, PRL. {\bf 127}, 197801 (2021)\\

\underline{P.W. Ellis}, J. Nambisan, A. Fern\'{a}ndez-Nieves, \emph{Coherence-enhanced diffusion filtering applied \\ \hspace*{15pt} to partially-ordered fluids}, Molecular Physics. {\bf 118}, e1725167 (2020)\\

\underline{P.W. Ellis}, S. Klane\u{c}ek, A. Fern\'{a}ndez-Nieves, \emph{Polarized epifluoresence microscopy and the \\ \hspace*{15pt} imaging of nematic liquid crystals in highly curved geometries}, PRE. {\bf 101}, 052703 (2020)\\

D.J.G. Pearce, \underline{P.W. Ellis}, A. Fern\'{a}ndez-Nieves, L. Giomi \emph{Geometrical control of active turbulence in \\ \hspace*{15pt} curved topographies}, PRL. {\bf 122}, 168002 (2019)\\

\underline{P.W. Ellis}, A. Fern\'{a}ndez-Nieves, \emph{Polarized optical microscopy textures of nematic liquid crystal tori}, \\ \hspace*{15pt} JPhys D. {\bf 52}, 213001 (2019)\\

J.P. McInerney, \underline{P.W. Ellis}, D.Z. Rocklin, A. Fern\'{a}ndez-Nieves, E.A. Matsumoto, \emph{Curved boundaries \\ \hspace*{15pt} and chiral instabilities --- two sources of twist in homeotropic nematic tori}, Soft Matter. (2019) \\

\underline{P.W. Ellis}, K. Nayani, J.P. McInerney, D.Z. Rocklin, M. Srinivasarao, E.A. Matsumoto, \\ \hspace*{15pt} A. Fern\'{a}ndez-Nieves, \emph{Curvature-induced twist in homeotropic nematics}, PRL. {\bf 121}, 247803 (2018) \\

\underline{P.W. Ellis}, S. Huang, S. Klane\u{c}ek, J. Vallamkondu, E. Dannemiller, M. Vernon, Y.W. Chang, \\ \hspace*{15pt} P.M. Goldbart, A. Fern\'{a}ndez-Nieves, \emph{Defect transitions in nematic liquid crystal capillary bridges},\\ \hspace*{15pt} PRE. {\bf 97}, 040701(R) (2018)\\

\newpage

\underline{P.W. Ellis}, D.J.G. Pearce, Y.W. Chang, G. Goldsztein, L. Giomi, A. Fern\'{a}ndez-Nieves, \emph{Curvature-induced \\ \hspace*{15pt} defect unbinding and dynamics in active nematic toroids}, Nat. Phys. {\bf 14}, 85 (2018) \\

K. Nayani, R. Chang, J. Fu, \underline{P.W. Ellis}, A. Fern\'{a}ndez-Nieves, J.O. Park, M. Srinivasarao, \emph{Spontaneous \\ \hspace*{15pt} emergence of chirality in achiral lyotropic chromonic liquid crystals confined to cylinders}, Nat. Comm. \\ \hspace*{15pt} {\bf 6}, 8067 (2015)  \\

A. Fragkopoulos, \underline{P.W. Ellis}, A. Fern\'{a}ndez-Nieves, \emph{Teaching Rayleigh-Plateau instabilities in the lab}, \\ \hspace*{15pt}EJP. {\bf 36}, 055023 (2015) \\

E. Pairam, J. Vallamkondu, V. Koning, B. C. van Zuiden, \underline{P. W. Ellis}, M. A. Bates, V. Vitelli, \\ \hspace*{15pt}A. Fern\'{a}ndez-Nieves, \emph{Stable nematic droplets with handles}, PNAS. {\bf 110}, 9295 (2013)\\

% K. Nayani, \underline{P.W. Ellis}, A. Fernandez-Nieves, M. Srinivasarao, \emph{The linear dependence of the \\ \hspace*{15pt} saddle-splay elastic constant on the scalar order parameter: unexpected transitions in nematic \\ \hspace*{15pt} droplets}. (In preparation)
\end{indentmore}

\textbf{\large PRESENTATIONS}
\begin{indentmore}
\emph{Better organoids through homogeneity}. \underline{P.W. Ellis}, G. Anand, Y.I. Yaman, D.A. Weitz, S. Ramanathan. \\ \hspace*{15pt} ISCCR 2020 Annual Meeting, Virtual Conference, June 23, 2020. Poster Presentation\\

\emph{Active nematics on a toroid: exploring the interactions between order, curvature, and activity}. \underline{P.W. Ellis}, \\ \hspace*{15pt} J. Nambisan, A. Fernandez-Nieves. Physics Colloquium, University of Massachusetts---Boston, \\ \hspace*{15pt} November 1, 2019. Oral Presentation\\

\emph{Active nematics on the surface of a toroid}. \underline{P.W. Ellis}, A. Fernandez-Nieves. Squishy Physics Seminar, \\ \hspace*{15pt} Harvard University, October 10, 2019. Oral Presentation\\

\emph{Defects in an active nematic confined to a toroid}. \underline{P.W. Ellis}, D. Pearce, L. Giomi, and A. Fernandez- \\ \hspace*{15pt} Nieves. Soft Matter Forefronts, Georgia Institute of Technology, April 18, 2019. Oral Presentation\\

\emph{Defects in an active nematic confined to a toroid}. \underline{P.W. Ellis}, D. Pearce, L. Giomi, and \\ \hspace*{15pt} A. Fernandez-Nieves. APS March Meeting, March 8, 2018. Oral Presentation\\

\emph{Defects in an active nematic confined to a toroid}. \underline{P.W. Ellis}, D. Pearce, L. Giomi, and \\ \hspace*{15pt} A. Fernandez-Nieves. APS March Meeting, March 16, 2017. Oral Presentation\\

\emph{Defect unbinding in active nematic toroids}. \underline{P.W. Ellis}, Y.W. Chang, and A. Fernandez-Nieves. ACS\\ \hspace*{15pt} Colloids and Surface Science Symposium, June 6, 2016. Oral Presentation\\

\emph{Active nematics on the surface of as torus}. \underline{P.W. Ellis}, Y.W. Chang, and A. Fernandez-Nieves. APS\\ \hspace*{15pt} March Meeting, March 14, 2016. Oral Presentation\\

\emph{Simulated textures of toroidal nematic liquid crystal droplets}. \underline{P.W. Ellis} and A. Fernandez-Nieves. ACS\\ \hspace*{15pt} Colloids and Surface Symposium, June 2014. Poster Presentation\\

\emph{Simulated textures of toroidal nematic liquid crystal droplets}. \underline{P.W. Ellis} and A. Fernandez-Nieves. APS\\ \hspace*{15pt} March Meeting, March 4 2014. Oral Presentation\\

\emph{Simulating nematic textures using Jones Matrices}. \underline{P.W. Ellis} and A. Fernandez-Nieves. Soft matter bag\\ \hspace*{15pt} lunch, Georgia Institute of Technology, November 13 2013. Oral Presentation\\
\end{indentmore}

% \vspace{10pt}
% \textbf{\large SKILLS}
% \begin{indentmore}
% Matlab  $\bullet$ Python $\bullet$ C $\bullet$ Mathematica $\bullet$
% Origin
% %SolidWorks $\bullet$
% %SolidEdge $\bullet$ COMSOL $\bullet$ LabVIEW
% $\bullet$ Adobe Illustrator $\bullet$ LaTeX $\bullet$ Microsoft Office $\bullet$ Linux $\bullet$ C $\bullet$  Written and Spoken Spanish.
% %$\bullet$ Igor
% \end{indentmore}
% \vspace{10pt}

% \textbf{\large TECHNICAL EQUIPMENT EXPERIENCE}
% \begin{indentmore}
% Optical Microscopy (bright field, crossed polarizers, fluorescence and fluorescence confocal)
% $\bullet$ Microfluidic Systems (generation of monodisperse single emulsions)
% $\bullet$ Pulsed and Continuous Wave Laser Systems (maintenance and use)
% $\bullet$ Machining and Fabrication (mill, lathe, 3D printing)
% %$\bullet$ Optical Coherence Tomography (use)
% $\bullet$ High Vacuum Systems (design, maintenance, and use)
% $\bullet$ High Voltage Systems (use)
% \end{indentmore}
% \vspace{10pt}

\textbf{\large PROJECT AND RESEARCH EXPERIENCE}\\
{\bf Postdoctoral Fellow}, Harvard University, Cambridge, MA \hfill Jan 2022 -- Present\\
\hspace*{10pt}$\bullet$ Develop a droplet microfluidic workflow for deep mutational scanning of enzymes\\
\hspace*{10pt}$\bullet$ Design and optimize multi-injector picoinjection chip \\
\hspace*{10pt}$\bullet$ Categorize mutations as deleterious, neutral, or beneficial for a library of $10^6$ mutations in under an hour.\\

\newpage

{\bf Postdoctoral Fellow}, Harvard University, Cambridge, MA \hfill Fall 2019 -- Present\\
\hspace*{10pt}$\bullet$ Develop a high-throughput droplet microfluidic workflow to improve organoid homogeneity\\
\hspace*{10pt}$\bullet$ Design and validate encapsulation, droplet sorting, and organoid deposition protocols and chips \\ \hspace*{15pt} compatible with human embryonic stem cells and primary cell lines\\
\hspace*{10pt}$\bullet$ Sort potential organoids based on starting cell composition and deposit organoids for long-term culture\\

{\bf Postdoctoral Fellow}, Harvard University, Cambridge, MA \hfill Jan 2021 -- Present\\
\hspace*{10pt}$\bullet$ Investigate the role of droplet size in a digital-droplet-LAMP (ddLAMP) assay for SARS-CoV-2\\
\hspace*{10pt}$\bullet$ Design and build a detection setup to record real-time amplification for ddLAMP\\
\hspace*{10pt}$\bullet$ Convert standard real-time-LAMP assays to be compatible with ddLMAP.\\
\hspace*{10pt}$\bullet$ Publication in preparation\\

{\bf Postdoctoral Fellow}, Harvard University, Cambridge, MA \hfill Fall 2019 -- Present\\
\hspace*{10pt}$\bullet$ Develop a droplet microfluidic assay to screen and sort cytotoxic bacteria from a mixed bacterial sample.\\
\hspace*{10pt}$\bullet$ Design and build a droplet sorting stand with 5 fluorescent channels and custom operating software.\\
\hspace*{10pt}$\bullet$ Design and optimize a microfluidic chip to robustly sort large droplets at high throughput\\
\hspace*{10pt}$\bullet$ Publication in preparation\\

{\bf Graduate Researcher}, Georgia Institute of Technology, Atlanta, GA \hfill Spring 2015 -- Spring 2018\\
\hspace*{10pt}$\bullet$ Use fluorescence confocal microscopy to study an active nematic liquid crystal confined to a toroidal\\ \hspace*{15pt} surface\\
\hspace*{10pt}$\bullet$ See defect density dependence on the local Gaussian curvature, the activity, and the toroid aspect ratio\\
\hspace*{10pt}$\bullet$ See curvature-induced defect unbinding in the time-averaged defect charge\\

{\bf Graduate Researcher}, Georgia Institute of Technology, Atlanta, GA \hfill Fall 2014 -- Spring 2018\\
\hspace*{10pt}$\bullet$ Investigate nematic liquid crystal confined to a toroidal droplet with homeotropic boundary conditions\\
\hspace*{10pt}$\bullet$ Use optical microscopy and simulation to investigate the role of curvature in the defect and director\\ \hspace*{15pt} configuration\\
\hspace*{10pt}$\bullet$ Find a structural transition away from an escaped radial configuration depending on the aspect ratio of\\ \hspace*{15pt} the toroidal droplet\\

{\bf Graduate Researcher}, Georgia Institute of Technology, Atlanta, GA \hfill Spring 2014 -- Spring 2018\\
\hspace*{10pt}$\bullet$ Investigate nematic liquid crystal confined between parallel plates with variable separation\\
\hspace*{10pt}$\bullet$ Use polarized microscopy, fluorescence microscopy, and simulation to determine defect \\ \hspace*{15pt} structure and type as a function of plate separation and droplet volume\\
\hspace*{10pt}$\bullet$ Find a transition between a ring defect and a point defect depending on bridge aspect ratio\\
\hspace*{10pt}$\bullet$ Find that the Gaussian curvature of the free surface of the liquid crystal determines the sign of the defect\\


{\bf Graduate Researcher}, Georgia Institute of Technology, Atlanta, GA \hfill Fall 2012 -- Spring 2018\\
\hspace*{10pt}$\bullet$ Simulate nematic textures based on a given director field and confining geometry.\\
\hspace*{10pt}$\bullet$ Used simulation in conjunction with experimental results to confirm a director hypothesis for \\ \hspace*{15pt} toroidal nematic liquid crystal droplets.\\

%{\bf Graduate Researcher}, Georgia Institute of Technology, Atlanta, GA \hfill Spring 2012 - Fall 2012\\
%\hspace*{10pt}$\bullet$ Investigated defect transitions in radial nematic liquid crystal droplets under internal flow.\\
%\hspace*{10pt}$\bullet$ Showed the transition from a radial droplet to an axial droplet is not guaranteed under internal flow.\\

{\bf Lawrence Livermore National Laboratory Clinic Team}, Claremont, CA \hfill Fall 2010 -- Spring 2011\\
\hspace*{10pt}$\bullet$ Developed a test bed to evaluate the photocathode for a dynamic transmission electron \\ \hspace*{15pt} microscope in order to overcome limiting factors in the current setup.\\
%$\bullet$ Optimize the photocathode material, shape and placement for a DTEM. \\
\hspace*{10pt}$\bullet$ Served as team leader: managed the four-person team and interacted with the project liaisons.\\


%{\bf Undergraduate Researcher}, Harvey Mudd College, Claremont, CA \hfill Summer 2010 \\
%$\bullet$ Worked as a member of a two-person team to characterize the binding of antibodies to gold nanospheres\\ \hspace*{5pt} in order to mark growing corneal cells. \\
%$\bullet$ Used Optical Coherence Tomography to assay phenotype expression of marked corneal tissue \textit{in vivo} as \\
%\hspace*{5pt} part of a larger corneal engineering project.\\
%\newpage

%{\bf Undergraduate Researcher}, Harvey Mudd College, Claremont, CA \hfill Fall 2009 \\
%$\bullet$ Designed and built an apparatus to produce high energy electrons via pulling Scotch sticky-tape in a \\ \hspace*{5pt} vacuum. \\
%$\bullet$ Designed a mechanical system to measure the spectrum of the emitted electrons from the sticky-tape \\ \hspace*{5pt} apparatus  \\
%\newpage
%{\bf Undergraduate Researcher}, SLAC National Accelerator Laboratory, Claremont, CA \hfill Summer 2009 \\
%$\bullet$ Collaborated as a member of a team to design and implement a GUI in Python for particle analysis for\\
%\hspace*{5pt} the BaBar Collaboration. \\

%{\bf Undergraduate Researcher}, Harvey Mudd College, Claremont, CA \hfill Spring 2009 \\
%$\bullet$  Collaborated as a member of a two person team to perform searches and measurements of baryons using \\ \hspace*{5pt} ROOT. \\

%{\bf Shop Proctor}, Harvey Mudd College	, Claremont, CA \hfill Fall 2008 - Spring 2009 \\
%$\bullet$ Helped other students fabricate their projects in the machine and wood shop. \\
%$\bullet$ Supervised safety in the student machine shop. \\




%{\bf Grader}, HMC Physics Department, Claremont, CA \hfill Spring 2009 \\
%$\bullet$ Graded homework assignments for Physics 51, Calculus based Electricity and Magnetism. \\


\textbf{\large TEACHING EXPERIENCE} \\
{\bf Graduate Teaching Assistant}, Georgia Institute of Technology, Atlanta, GA \hfill Fall 2013 -- Spring 2014\\
\hspace*{10pt}$\bullet$ Develop a laboratory section for a future graduate course in Soft Condensed Matter.  \\
\hspace*{10pt}$\bullet$ Designed lab experiments to introduce the student to important broad concepts in Soft Condensed \\ \hspace*{15pt} Matter while developing critical thinking and experimental technique.  \\

\newpage

{\bf Graduate Teaching Assistant}, Georgia Institute of Technology, Atlanta, GA \hfill Spring 2013 -- Summer 2013\\
\hspace*{10pt}$\bullet$ Developed a laboratory section for a future class, P21CS, Physics for 21$^{st}$ Century Students. \\
\hspace*{10pt}$\bullet$ Designed course to impart an intuitive understanding of basic physics concepts relevant for the \\ \hspace*{15pt} modern citizen without focusing on the math. \\

{\bf Graduate Teaching Assistant}, Georgia Institute of Technology, Atlanta, GA \hfill Fall 2012 \\
\hspace*{10pt}$\bullet$ Lectured, held office hours, and graded homework and exams for Physics 3141, Thermodynamics. \\


{\bf Graduate Teaching Assistant}, Georgia Institute of Technology, Atlanta, GA \hfill Fall 2011 -- Summer 2011\\
\hspace*{10pt}$\bullet$ Taught laboratory and recitation sections, tutored students, and graded exams for Physics 2211, \\ \hspace*{15pt} Calculus-based Mechanics. \\


{\bf  Graduate Teaching Assistant}, Scripps College, Claremont, CA \hfill Summer 2011\\
\hspace*{10pt}$\bullet$ Assisted with laboratory sessions, tutored students, and graded homework assignments for General\\ \hspace*{15pt} Physics 31, Calculus-based Electricity and Magnetism. \\


%
%\textbf{\large ACTIVITIES} \\
%{\bf Water Polo}, Laguna Hills, CA \& Claremont, CA \hfill Fall 2002 - Fall 2009 \\
%$\bullet$ Played as a member of high school and college varsity programs. \\
%$\bullet$ Competed up to national levels in high school and college.\\
%
%{\bf Swimming}, Laguna Hills, CA \& Claremont, CA \hfill Spring 2003 - Spring 2008 \\
%$\bullet$ Competed for high school and college varsity programs. Competed up to state and conference levels.\\
%
%
%{\bf brewSHMC}, Claremont, CA \hfill Summer 2008 - Spring 2011 \\
%$\bullet$ Founding co-president of the Harvey Mudd College Brewing Club. \\
%$\bullet$ Managed and oversaw 20 members who enjoyed brewing beer. \\


\textbf{\large SERVICE}\\
{\bf Professional Service}
\begin{indentmore}
{\bf Journal referee}, \hfill Fall 2018 -- Present
\begin{indentmore}
$\bullet$ Served as referee for Physical Review Letters, Physical Review E, and Journal of Molecular Liquids\\
$\bullet$ Evaluated submitted manuscripts for scientific merit, clarity, and validity\\
\end{indentmore}

{\bf PURA reviewer}, Georgia Institute of Technology, Atlanta, GA \hfill Spring 2013 - Spring 2018
\begin{indentmore}
$\bullet$ Reviewed applicants for the President's Undergraduate Research Awards (PURA), a program funding \\ \hspace*{5pt} undergraduate research under a faculty mentor.\\
$\bullet$ Evaluated applications on scientific merit, student ability, and faculty endorsement of the student.\\
\end{indentmore}
\end{indentmore}


{\bf Community Service}
\begin{indentmore}
{\bf Member of Gamma Beta Phi}, Georgia Institute of Technology, Atlanta, GA \hfill Summer 2012 -- Spring 2014
\begin{indentmore}
$\bullet$ A national honor society focused on community service. \\
\end{indentmore}
\end{indentmore}

\textbf{\large HOBBIES} \\
 Cooking $\bullet$ Rock Climbing $\bullet$ Brazilian Jiu-Jitsu $\bullet$  Tabletop Games $\bullet$ Water Polo $\bullet$ Hiking $\bullet$ Swimming



\end{document}
